Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2018-05-24 manuscript.tex

        \caption{\( L_1 \) Reachability set transfer: The low thrust propulsion is used to approximate the reachability set starting from the initial periodic orbit over a fixed time horizon.
        The reachability set is shown in the upper two figures in both the position and \Poincare space.
    From this reachability set we chose a trajectory which intersects the target orbit and it is shown in the lower left figure.
The optimal control to achieve this transfer is shown in the lower right figure.}
        \label{fig:reachability_set_transfer} 
\end{figure}

% generate the optimal transfer
\Cref{fig:poincare_compare} shows that the reachable set and those of the descending target region intersect.
As both regions are discretely approximated a linear interpolation is used to determine the exact intersection state on the \Poincare section.
This intersection generates a partial target state of \( x_t \text{ and } \dot{x}_t \).
Using the energy level of the target region, defined by~\cref{eq:jacobi}, and the intersection state we can calculate the final component \( \dot{y} \) is calculated. 
This results in a complete target state \( \vecbf{x}_t \) which lies on the reachable set and on the target orbit. 
A final optimal trajectory is generated such that the \( \vecbf{x}(N) = \vecbf{x}_t \).
This transfer trajectory is denoted by the green path in~\cref{fig:reach_transfer}.
The optimal control input is shown in~\cref{fig:control_l1}. 
The spacecraft achieves the desired target while satisfying the bounded control input.
The Jacobi energy integral, computed using~\cref{eq:jacobi}, is shown in~\cref{fig:jacobi_l1}.
\Cref{fig:jacobi_l1} shows that the vehicle begins with an energy level equal to the periodic orbit and arrives at the target orbit with the appropriate energy.
The first half of the transfer is associated with and increase in energy as the control is used to transition towards the target orbit which is followed by a energy decrease to the target orbit.
This roughly corresponds with the expected optimal solution of a bang-coast-bang type orbital transfer~\cite{kirk2012}.
Convergence statistics associated for this transfer are shown in~\cref{tab:l1_transfer_stats}.
\begin{table}
    \centering
    \begin{tabular}{llr}  
        \toprule
        Metric    & Value \\
        \midrule
        \texttt{fsolve} objective      & \num{6.03e-15}      \\
        \texttt{fsolve} major iterations       & \num{9}      \\
        \texttt{fsolve} first order optimality & \num{1.88e-13} \\
        Optimal cost       & \num{2.09e-31}      \\
        Execution time & \SI{1.49}{\second}       \\
        \bottomrule

>>>>

        \caption{\( L_1 \) Reachability set transfer: The low thrust propulsion is used to approximate the reachability set starting from the initial periodic orbit over a fixed time horizon.
            The reachability set is shown in~\cref{fig:reach_trajectory,fig:poincare_compare} in both the position and \Poincare space respectively.
            From this reachability set we chose a trajectory which intersects the target orbit and it is shown in~\cref{fig:reach_transfer}.
        The optimal control to achieve this transfer is shown in~\cref{fig:control_l1}.}
        \label{fig:reachability_set_transfer} 
\end{figure}

% generate the optimal transfer
\Cref{fig:poincare_compare} shows that the reachable set and those of the descending target region intersect.
As both regions are discretely approximated a linear interpolation is used to determine the exact intersection state on the \Poincare section.
This intersection generates a partial target state of \( x_t \text{ and } \dot{x}_t \).
Using the energy level of the target region, defined by~\cref{eq:jacobi}, and the intersection state we can calculate the final component \( \dot{y} \). 
This results in a complete target state \( \vecbf{x}_t \) which lies on the reachable set and on the target orbit. 
A final optimal trajectory is generated such that the \( \vecbf{x}(N) = \vecbf{x}_t \).
This transfer trajectory is denoted by the green path in~\cref{fig:reach_transfer}.
The optimal control input is shown in~\cref{fig:control_l1}. 
The spacecraft achieves the desired target while satisfying the bounded control input.
The Jacobi energy integral, computed using~\cref{eq:jacobi}, is shown in~\cref{fig:jacobi_l1}.
\Cref{fig:jacobi_l1} shows that the vehicle begins with an energy level equal to the periodic orbit and arrives at the target orbit with the appropriate energy.
The first half of the transfer is associated with and increase in energy as the control is used to transition towards the target orbit which is followed by a energy decrease to the target orbit.
This roughly corresponds with the expected optimal solution of a bang-coast-bang type orbital transfer~\cite{kirk2012}.
Convergence statistics associated for this transfer are shown in~\cref{tab:l1_transfer_stats}.
\begin{table}
    \centering
    \begin{tabular}{llr}  
        \toprule
        Metric    & Value \\
        \midrule
        \texttt{fsolve} objective      & \num{6.03e-15}      \\
        \texttt{fsolve} major iterations       & \num{9}      \\
        \texttt{fsolve} first order optimality & \num{1.88e-13} \\
        Optimal cost       & \num{2.09e-31}      \\
        Execution time & \SI{1.49}{\second}       \\
        \bottomrule
